---
title: "OrganicChemistryUnknown_progress_report"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

The purpose of the project is to generate a search engine that will assist in narrowing the list of OBU organic unknowns based off of the following criteria:melting point, boiling point, whether the compound is a solid or liqid at room temperature, and high priority functional groups. The project will contain 3 main phases that are listed as followed.

Phase 1: compilation of data to satisfy the criteria needed to generate an output.

Phase 2: organization of the compiled data via tidy data standards, in order to finalize the database.

Phase 3: joining the data in an SQL process.

Phase 4: creation of the of the webpage and generating the interface.

The group is currently in phase 1 and the work shall be divided by inividually compiling the data by functional group. Listed below is the division of functional groups by group member:

Rachel: acetals, acid anyhydrides, acid halides, alcohols, aldehydes, alkanes, alkenes, amines, arylalkanes, and AzoCompounds

Jake: Amides; HeterocyclicCompounds; Hydrazines,Hydrazides; Imides; Ketones; Nitrates,Nitrites; Nitriles; Nitro-containingCompounds; Oximes; Phenols; PhosphorousCompounds


Devin: Quinones; Sulfates; Sulfides; Sulfocompounds; Thiols; Ureas; Monomers for polymers; Misc. compounds



Reid: carbamates; carbanilides; carbohydrates; carboxylicacids; cyanates; isoesters; thioesters; ethers; guanidines

Resources:
https://pubchem.ncbi.nlm.nih.gov/
https://www.chemicalbook.com/.
https://www.sigmaaldrich.com/US.
https://www.fishersci.com/ 
https://stackoverflow.com/
https://en.wikipedia.org/
all information is currently being entered into an excel spreadsheet; all questions are being presented to Dr. Malmberg along with the course guidline materials.

Responsibilites for each phase to follow will be assigned after meeting with Dr. Malmberg.
```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
